The interactions of rational, pragmatic agents\\ lead to efficient language structure and use

### 2019-01-30 paper/paper.Rmd
update context plot with new n=500 run

```{r plot-optimal-langs, fig.env = "figure*", fig.pos = "h", fig.width=8, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases. Vertical axis shows the proportion of optimal languages that contain ambiguity. Horizontal axis shows the number of contexts in each condition (1-4). Red-line represents the optimal language under our Zipfian cross-entropy objective while the blue and red lines show optimal languages under speaker- and listener-only objectives."}
img <- png::readPNG("figs/fig1.png")
grid::grid.raster(img)
```

@@

```{r plot-optimal-use, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=2.5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) shows the empirical probability that our speaker used an ambiguous utterance as a function of discourse position. (B) shows speaker effort across the three models. (C) shows the Cross-Entropy objective under our three speaker models."}

>>>>

```{r plot-optimal-langs, fig.env = "figure*", fig.pos = "h", fig.width=8, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases. Vertical axis shows the proportion of optimal languages that contain ambiguity. Horizontal axis shows the number of contexts in each condition (1-4). Red-line represents the optimal language under our Zipfian cross-entropy objective while the blue and red lines show optimal languages under speaker- and listener-only objectives. Error bars represent 95% confidence intervals."}
img <- png::readPNG("figs/fig1.png")
grid::grid.raster(img)
```

@@

```{r plot-optimal-use, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=2.5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) shows the empirical probability that our speaker used an ambiguous utterance as a function of discourse position. (B) shows speaker effort across the three models. (C) shows the Cross-Entropy objective under our three speaker models. Error bars represent 95% confidence intervals."}

### 2019-01-30 paper/paper.tex
update context plot with new n=500 run

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/plot-optimal-langs-1}

\caption[Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases]{Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases. Vertical axis shows the proportion of optimal languages that contain ambiguity. Horizontal axis shows the number of contexts in each condition (1-4). Red-line represents the optimal language under our Zipfian cross-entropy objective while the blue and red lines show optimal languages under speaker- and listener-only objectives.}\label{fig:plot-optimal-langs}
\end{figure*}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/plot-optimal-use-1}

\caption[(A) shows the empirical probability that our speaker used an ambiguous utterance as a function of discourse position]{(A) shows the empirical probability that our speaker used an ambiguous utterance as a function of discourse position. (B) shows speaker effort across the three models. (C) shows the Cross-Entropy objective under our three speaker models.}\label{fig:plot-optimal-use}
\end{figure*}
\end{CodeChunk}

>>>>

\textbackslash{}begin\{CodeChunk\}
\textbackslash{}begin\{figure*\}{[}h{]}

\{\centering \includegraphics{figs/plot-optimal-langs-1}

\}

\textbackslash{}caption{[}Optimal languages are more likely to contain
ambiguous items as the amount of contextual information
increases{]}\{Optimal languages are more likely to contain ambiguous
items as the amount of contextual information increases. Vertical axis
shows the proportion of optimal languages that contain ambiguity.
Horizontal axis shows the number of contexts in each condition (1-4).
Red-line represents the optimal language under our Zipfian cross-entropy
objective while the blue and red lines show optimal languages under
speaker- and listener-only objectives. Error bars represent 95\%
confidence intervals.\}\label{fig:plot-optimal-langs}
\textbackslash{}end\{figure*\} \textbackslash{}end\{CodeChunk\}

@@

\textbackslash{}begin\{CodeChunk\}
\textbackslash{}begin\{figure*\}{[}h{]}

\{\centering \includegraphics{figs/plot-optimal-use-1}

\}

\textbackslash{}caption{[}(A) shows the empirical probability that our
speaker used an ambiguous utterance as a function of discourse
position{]}\{(A) shows the empirical probability that our speaker used
an ambiguous utterance as a function of discourse position. (B) shows
speaker effort across the three models. (C) shows the Cross-Entropy
objective under our three speaker models. Error bars represent 95\%
confidence intervals.\}\label{fig:plot-optimal-use}
\textbackslash{}end\{figure*\} \textbackslash{}end\{CodeChunk\}
